---
title: "SOHO100"
format: 
  html:
      toc: true
---

# Who

You!

# What

The SOHO 100 is the first edition of the South Hobart Metrogaine/Scavenger hunt! A metrogaine is a form or [rogaine](https://rogaine.asn.au/about/what-is-rogaining) held in an urban environment.

The goal is to get the most number of points.

You get points by visiting the locations, which we call, "controls", which marked on the map.

To verify that you have visited a location, there are "found items" on most controls

There are also bonus points available on many controls.


# Where / When

Fruehoff at 11am

```{r}
#| echo: false
library(leaflet)
leaflet() |> 
    addTiles() |> 
    addMarkers(lng = 147.3012348499976,
               lat = -42.893349257964054) |> 
     addPopups(lng = 147.3012348499976,
               lat = -42.893349257964054,
               popup = 'Here is the where the <b>SOHO 100 begins!</b>')
```

# Why?

It was created by Nick as a way to do something fun for his friends.

# How?

The event will run by 

# Map

You can download the map by clicking the links below

- [SOHO 100 map](soho-100-35.pdf)

# Clue sheet

You can download the clue sheet below:

- [clue sheet 2 pages](soho-100-35-clues.pdf)
- [clue sheet 1 page](soho-100-35-clues-2p.pdf)

You can also see the clue sheet at this table below:

```{r}
library(tidyverse)

soho100 <- read_csv("soho-100-data.csv",
                    show_col_types = FALSE,
                    n_max = 32)

DT::datatable(soho100,
              options = list(
                  pageLength = 33
              ))
```


# Bonus point multiplies

* Visit all cafes on the list = 30 points. (Hamlet, Pigeon Whole, Pigeon Hole)
* Rock Soup =  40 points. Bring two soup vegetables to Preachers.
* Pigeon bonus = 20 points. Visit pigeon Hole and Pigeon Whole
* Echidna bonus: 10 points. if you see a (live) Echidna
* Monotreme bonus:  1000 points for seeing both a platypus and eechidna


# Transport multiplies

* Horseback = 25x total points
* On Foot = 10x total points
* Cycling = 5x total points
* Car = 1x total points
* % of each also allowed
